---
title: "lungcancer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lungcancer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(funkycells)
```

```{r define_vars, echo=FALSE}
full_run <- FALSE # This runs only computations that are feasibly quick
```

This vignette gives the code used to analyze the lung cancer data. However, due to data privacy, that data is not yet available in package. This is being investigated and we hope future version of the package include this data.
```{r load_data, eval=FALSE}
dat <- lungcancer
```

This data is pre-processed and thus we only need to complete a few steps. But to aid in these, we define a few functions.
```{r define_functions, eval=FALSE}
getInteractions <- function(cells,
                            dropCells = c(
                              "Epithelialcells",
                              "Stromalcells", "Other"
                            )) {
  cells <- cells[!(cells %in% dropCells)]
  return_df <- data.frame("c1" = cells[1], "c2" = cells[1])
  if (length(cells) > 1) {
    return_df <- rbind(
      data.frame(t(combn(cells, 2))),
      data.frame("X1" = cells, "X2" = cells)
    )
  }

  return_df
}

clean_figures <- function(model_rf) {
  specify_decimal <- .specify_decimal
  # Get Vars
  viData <- model_rf$VariableImportance
  accData <- model_rf$AccuracyEstimate
  NoiseCutoff <- model_rf$NoiseCutoff
  InterpolationCutoff <- model_rf$InterpolationCutoff
  subsetPlotSize <- model_rf$AdditionalParams$subsetPlotSize

  # Plot Full
  maxVal <- max(InterpolationCutoff, NoiseCutoff, viData$est)
  sub_val <- paste0(
      "OOB (",
      specify_decimal(accData$OOB, 2),
      "), Guess (",
      specify_decimal(accData$guess, 2),
      "), Bias (",
      specify_decimal(accData$bias, 2), ")"
  )
  plot_full <- ggplot2::ggplot(
    data = viData,
    mapping = ggplot2::aes(
      x = factor(stats::reorder(var, est)),
      y = ifelse(est / maxVal > 1, 1,
        ifelse(est / maxVal < 0, 0,
          est / maxVal
        )
      ),
      group = 1
    )
  ) +
    ggplot2::geom_errorbar(
      ggplot2::aes(
        ymin = ifelse((est - sd) / maxVal < 0, 0, (est - sd) / maxVal),
        ymax = ifelse((est + sd) / maxVal > 1, 1, (est + sd) / maxVal)
      ),
      color = "black", width = 0.2
    ) +
    ggplot2::geom_point(color = "black", size = 3) +
    ggplot2::geom_hline(
      ggplot2::aes(yintercept = max(0, min(1, NoiseCutoff / maxVal))),
      color = "red", linetype = "dotted", linewidth = 2
    ) +
    ggplot2::coord_flip(ylim = c(0, 1)) +
    ggplot2::xlab(NULL) +
    ggplot2::ylim(c(0, 1)) +
    ggplot2::ylab(NULL) +
    ggplot2::theme_bw() +
    ggplot2::theme(
      axis.text.y = ggplot2::element_blank(),
      axis.text.x = ggplot2::element_text(size = 14),
      axis.ticks.y = ggplot2::element_blank(),
      panel.grid.major.y = ggplot2::element_blank(),
      axis.title = ggplot2::element_text(size = 20)
    ) +
    ggplot2::geom_line(ggplot2::aes(
      x = ordered(viData[order(-est), "var"]),
      y = InterpolationCutoff / maxVal
    ), color = "orange", linetype = "dashed", linewidth = 2) +
    ggplot2::ylab(bquote(atop(bold("Standardized Variable Importance"),
                            atop(italic(.(sub_val))))))
   

  # Plot Subset
  InterpolationCutoff1 <- InterpolationCutoff[1:subsetPlotSize]
  viData1 <- viData[order(-viData$est), ]
  viData1 <- viData1[1:subsetPlotSize, ]

  maxVal <- max(InterpolationCutoff1, NoiseCutoff, viData1$est)
  sub_val <- paste0(
      "OOB (",
      specify_decimal(accData$OOB, 2),
      "), Guess (",
      specify_decimal(accData$guess, 2),
      "), Bias (",
      specify_decimal(accData$bias, 2), ")"
  )
  plot_top25 <- ggplot2::ggplot(
    data = viData1,
    mapping = ggplot2::aes(
      x = factor(stats::reorder(var, est)),
      y = ifelse(est / maxVal > 1, 1,
        ifelse(est / maxVal < 0, 0,
          est / maxVal
        )
      ),
      group = 1
    )
  ) +
    ggplot2::geom_errorbar(
      ggplot2::aes(
        ymin = ifelse((est - sd) / maxVal < 0, 0, (est - sd) / maxVal),
        ymax = ifelse((est + sd) / maxVal > 1, 1, (est + sd) / maxVal)
      ),
      color = "black", width = 0.2
    ) +
    ggplot2::geom_point(color = "black", size = 3) +
    ggplot2::geom_hline(
      ggplot2::aes(yintercept = max(0, min(1, NoiseCutoff / maxVal))),
      color = "red", linetype = "dotted", linewidth = 2
    ) +
    ggplot2::coord_flip(ylim = c(0, 1)) +
    ggplot2::xlab(NULL) +
    ggplot2::ylim(c(0, 1)) +
    ggplot2::ylab(NULL) +
    ggplot2::theme_bw() +
  ggplot2::theme(
    axis.text.y = ggplot2::element_text(size = 16),
    axis.text.x = ggplot2::element_text(size = 14),
    axis.ticks.y = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    axis.title = ggplot2::element_text(size = 16)
  ) +
    ggplot2::geom_line(ggplot2::aes(
      x = ordered(viData1[order(-est), "var"]),
      y = InterpolationCutoff1 / maxVal
    ), color = "orange", linetype = "dashed", linewidth = 2) +
    ggplot2::ylab(bquote(atop(bold("Standardized Variable Importance"),
                            atop(italic(.(sub_val))))))

  list(
    "full" = plot_full,
    "top" = plot_top25
  )
}

```

The data must be converted to $K$ functions, then to in finite dimensions. This data is then combined with the smoking meta-data.
```{r pca_data, eval=full_run}
pcaData <- getKsPCAData(
  data = dat[!(colnames(dat) %in% c("SmokingStatusLong"))],
  outcome = "Cancer",
  unit = "Patient",
  replicate = "Image",
  rCheckVals = seq(0, 50, 1),
  nPCs = 3,
  agents_df = getInteractions(unique(dat$cellType)),
  displayTVE = FALSE
)

data_rf <- merge(pcaData,
  unique(dat[, c("Patient", "SmokingStatusLong")]),
  keep.x = TRUE, by.x = "Patient", by.y = "Patient"
)
```

And then we fit the model on the data:
```{r fit_model, eval=full_run}
set.seed(12345)
model_fm <- funkyModel(
  data = data_rf[!is.na(data_rf[["Cancer"]]), ],
  outcome = "Cancer", unit = "Patient",
  metaNames = "SmokingStatusLong"
)
```

The plots can be given as well:
```{r plot_data, eval=full_run}
figs <- clean_figures(model_fm)
figs$full
figs$top
```
