---
title: "model_walkthrough"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{model_walkthrough}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(funkycells)
```

```{r define_functions, echo=FALSE}
full_run <- FALSE # This runs only computations that are feasibly quick
paper_run <- FALSE # This creates and saves figures as in paper
save_path <- tempdir() # Save to temp directory as desired
specify_decimal <- function(x, k) {
  trimws(format(round(x, k), nsmall = k))
}
```

This vignettes walks through the approach `funkycells` takes to modeling data. The package `funkycells` is best employed when considering spatial data. While this data is typically collected, below such data is created. 
```{r build_data}
set.seed(123)
cell_data <- simulatePP(
  agentVarData =
    data.frame(
      "outcome" = c(0, 1),
      "A" = c(0, 0),
      "B" = c(1 / 100, 1 / 300)
    ),
  agentKappaData =
    data.frame(
      "agent" = c("A", "B"),
      "clusterAgent" = c(NA, "A"),
      "kappa" = c(20, 5)
    ),
  unitsPerOutcome = 15,
  replicatesPerUnit = 2,
  silent = FALSE
)
```

The created data has two outcomes ($0$ and $1$), and two cells ($A$ and $B$). The cells are constructed such that $A$ is completely spatial random and $B$ clusters around $A$. Moreover, $B$ has increased clustering in stage $1$ when compared to stage $0$. The data has $15$ patients in each stage, with $2$ images per patient. An example image for each stage is given below.
```{r show_spatial_images}
plotPP(cell_data[cell_data$replicate == 1, c("x", "y", "type")],
  ptSize = 2, colorGuide = ggplot2::guide_legend(title = "Cells"),
  xlim = c(0, 1), ylim = c(0, 1)
)

plotPP(cell_data[cell_data$replicate == 21, c("x", "y", "type")],
  ptSize = 2, colorGuide = ggplot2::guide_legend(title = "Cells"),
  xlim = c(0, 1), ylim = c(0, 1)
)
```

```{r paper_spatial_images, echo=FALSE, eval=paper_run}
img1 <- plotPP(
  data = cell_data[cell_data$replicate == 1, c("x", "y", "type")],
  ptSize = 3, dropAxes = T, colorGuide = "none"
)
png(paste0(save_path,"/paper/diagram_pp1.png"), width = 800, height = 800)
print(img1)
dev.off()

img21 <- plotPP(
  data = cell_data[cell_data$replicate == 21, c("x", "y", "type")],
  ptSize = 3, dropAxes = T, colorGuide = "none"
)
png(paste0(save_path,"/paper/diagram_pp21.png"), width = 800, height = 800)
print(img21)
dev.off()

img41 <- plotPP(
  data = cell_data[cell_data$replicate == 41, c("x", "y", "type")],
  ptSize = 3, dropAxes = T, colorGuide = "none"
)
png(paste0(save_path,"/paper/diagram_pp41.png"), width = 800, height = 800)
print(img41)
dev.off()
```

The next step is to summarize the functions. This is done through $2$-way interactions using $K$ functions. With only two cells, there are four possible interactions ($A$-$A$,$A$-$B$, $B$-$A$, and $B$-$B$). Often reverse interactions (i.e. $A$-$B$ and $B$-$A$) are highly related and so consideration of only one is encouraged to remove variables in the model and improve power. An example of the $K$ functions is given below.
```{r show_K_functions}
AB_ex <- getKFunction(
  cell_data[
    cell_data$replicate == 1,
    !(colnames(cell_data) %in% ("outcome"))
  ],
  agents = c("A", "B"), unit = "unit", replicate = "replicate",
  rCheckVals = seq(0, 0.25, 0.01), xRange = c(0, 1), yRange = c(0, 1)
)

ggplot2::ggplot() +
  ggplot2::geom_line(ggplot2::aes(x = r, y = K1), data = AB_ex, linewidth = 2) +
  ggplot2::theme_bw() +
  ggplot2::theme(
    axis.title = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank()
  )
```

```{r paper_K_functions, echo=FALSE, eval=paper_run}
AA_im1 <- getKFunction(
  cell_data[
    cell_data$replicate == 1,
    !(colnames(cell_data) %in% ("outcome"))
  ],
  agents = c("A", "A"), unit = "unit", replicate = "replicate",
  rCheckVals = seq(0, 0.25, 0.01), xRange = c(0, 1), yRange = c(0, 1)
)
AB_im1 <- getKFunction(
  cell_data[
    cell_data$replicate == 1,
    !(colnames(cell_data) %in% ("outcome"))
  ],
  agents = c("A", "B"), unit = "unit", replicate = "replicate",
  rCheckVals = seq(0, 0.25, 0.01), xRange = c(0, 1), yRange = c(0, 1)
)

AAfig_im1 <- ggplot2::ggplot() +
  ggplot2::geom_line(ggplot2::aes(x = r, y = K1), data = AA_im1, linewidth = 3) +
  ggplot2::theme_bw() +
  ggplot2::theme(
    axis.title = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank()
  )
png(paste0(save_path,"/paper/diagram_K_AA_i1.png"), width = 800, height = 800)
print(AAfig_im1)
dev.off()

ABfig_im1 <- ggplot2::ggplot() +
  ggplot2::geom_line(ggplot2::aes(x = r, y = K1), data = AB_im1, linewidth = 3) +
  ggplot2::theme_bw() +
  ggplot2::theme(
    axis.title = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank()
  )
png(paste0(save_path,"/paper/diagram_K_AB_i1.png"), width = 800, height = 800)
print(ABfig_im1)
dev.off()
```

These functions must then be projected into finite dimensions. Since $K$ functions are so commonly used, `funkycells` has a specialized function for computing and projecting the $K$ functions through the popular functional principle components analysis. The following code projects the functions into $3$ principle components each.
```{r pca}
pcaData <- getKsPCAData(
  data = cell_data, replicate = "replicate",
  agents_df = data.frame(c("A", "A", "B"), c("A", "B", "B")),
  xRange = c(0, 1), yRange = c(0, 1),
  nPCs = 3, silent = T
)
```

Often data is also collected with some meta-variables, such as with patient age or sex Both age and sex are simulated below. In the simulation, higher age is related to outcome $1$ while sex has no effect.
```{r simulate_meta}
set.seed(123)
pcaMeta <- simulateMeta(pcaData,
  metaInfo = data.frame(
    "var" = c("sex", "age"),
    "rdist" = c("rbinom", "rnorm"),
    "outcome_0" = c("0.5", "25"),
    "outcome_1" = c("0.5", "26")
  )
)
```

This data is fed into `funkyModel()` which adds synthetics and examines the variables efficacy in predicting the outcome.
```{r evaluate_model, eval=full_run | full_run}
set.seed(123)
model_fm <- funkyModel(
  data = pcaMeta,
  outcome = "outcome",
  unit = "unit",
  metaNames = c("sex", "age")
)
```

The model returns, in addition to other details, a variable importance plot. This plot can be used to compare efficacy of each variable in comparison to each other and random noise.
```{r show_variable_importance, eval=full_run}
model_fm$viPlot
```

```{r paper_variable_importance, echo=FALSE, eval=paper_run}
# Get Vars
viData <- model_fm$VariableImportance
accData <- model_fm$AccuracyEstimate
NoiseCutoff <- model_fm$NoiseCutoff
InterpolationCutoff <- model_fm$InterpolationCutoff

# Plot
maxVal <- max(InterpolationCutoff, NoiseCutoff, viData$est)
sub_val <- paste0(
    "OOB (",
    specify_decimal(accData$OOB, 2),
    "), Guess (",
    specify_decimal(accData$guess, 2),
    "), Bias (",
    specify_decimal(accData$bias, 2), ")"
)
plot_vi_full <- ggplot2::ggplot(
  data = viData,
  mapping = ggplot2::aes(
    x = factor(stats::reorder(var, est)),
    y = ifelse(est / maxVal > 1, 1,
      ifelse(est / maxVal < 0, 0,
        est / maxVal
      )
    ),
    group = 1
  )
) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      ymin = ifelse((est - sd) / maxVal < 0, 0, (est - sd) / maxVal),
      ymax = ifelse((est + sd) / maxVal > 1, 1, (est + sd) / maxVal)
    ),
    color = "black", width = 0.2
  ) +
  ggplot2::geom_point(color = "black", size = 3) +
  ggplot2::geom_hline(
    ggplot2::aes(yintercept = max(0, min(1, NoiseCutoff / maxVal))),
    color = "red", linetype = "dotted", linewidth = 2
  ) +
  ggplot2::coord_flip(ylim = c(0, 1)) +
  ggplot2::xlab(NULL) +
  ggplot2::ylim(c(0, 1)) +
  ggplot2::ylab(NULL) +
  ggplot2::theme_bw() +
  ggplot2::theme(
    axis.text.y = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_text(size = 14),
    axis.ticks.y = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    axis.title = ggplot2::element_text(size = 20)
  ) +
    ggplot2::geom_line(ggplot2::aes(
      x = ordered(viData[order(-est), "var"]),
      y = InterpolationCutoff / maxVal
    ), color = "orange", linetype = "dashed", linewidth = 2) +
    ggplot2::ylab(bquote(atop(bold("Standardized Variable Importance"),
                            atop(italic(.(sub_val))))))

png(paste0(save_path,"/paper/diagram_variableimportance.png"))
print(plot_vi_full)
dev.off()


# Plot
maxVal <- max(InterpolationCutoff, NoiseCutoff, viData$est)
sub_val <- paste0(
    "OOB (",
    specify_decimal(accData$OOB, 2),
    "), Guess (",
    specify_decimal(accData$guess, 2),
    "), Bias (",
    specify_decimal(accData$bias, 2), ")"
)
plot_vi_details <- ggplot2::ggplot(
  data = viData,
  mapping = ggplot2::aes(
    x = factor(stats::reorder(var, est)),
    y = ifelse(est / maxVal > 1, 1,
      ifelse(est / maxVal < 0, 0,
        est / maxVal
      )
    ),
    group = 1
  )
) +
  ggplot2::geom_errorbar(
    ggplot2::aes(
      ymin = ifelse((est - sd) / maxVal < 0, 0, (est - sd) / maxVal),
      ymax = ifelse((est + sd) / maxVal > 1, 1, (est + sd) / maxVal)
    ),
    color = "black", width = 0.2
  ) +
  ggplot2::geom_point(color = "black", size = 3) +
  ggplot2::geom_hline(
    ggplot2::aes(yintercept = max(0, min(1, NoiseCutoff / maxVal))),
    color = "red", linetype = "dotted", linewidth = 2
  ) +
  ggplot2::coord_flip(ylim = c(0, 1)) +
  ggplot2::xlab(NULL) +
  ggplot2::ylim(c(0, 1)) +
  ggplot2::ylab(NULL) +
  ggplot2::theme_bw() +
  ggplot2::theme(
    axis.text.y = ggplot2::element_text(size = 18),
    axis.text.x = ggplot2::element_text(size = 14),
    axis.ticks.y = ggplot2::element_blank(),
    panel.grid.major.y = ggplot2::element_blank(),
    axis.title = ggplot2::element_text(size = 20)
  ) +
    ggplot2::geom_line(ggplot2::aes(
      x = ordered(viData[order(-est), "var"]),
      y = InterpolationCutoff / maxVal
    ), color = "orange", linetype = "dashed", linewidth = 2) +
    ggplot2::ylab(bquote(atop(bold("Standardized Variable Importance"),
                            atop(italic(.(sub_val))))))

png(paste0(save_path,"/paper/diagram_variableimportance_names.png"))
print(plot_vi_details)
dev.off()
```
