---
title: "Performance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Performance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(funkycells)
library(tidyverse)
```


The following chunks of code look into the rate of detection for a significant interaction compared to the other non-significant interactions.

This first chunk is the function used to generate the data.
```{r gen_alt}
simulate_Data_numCells_alt <- function(seed=NA, numCells=1){
  ## SET SEED
  if(!is.na(seed)){
    set.seed(seed)
  }
  
  dat_use <- data.frame("outcome" = c(0, 1),
                        "c1" = c(1 / 40, 1 / (4*40)))
  kappas <- rep(NA,numCells)
  kappas[1] <- rbinom(1, 80, 0.5)
  for(i in 2:numCells){
    tmp_names <- colnames(dat_use)
    dat_use <- cbind(dat_use,c(1/40,1/40))
    colnames(dat_use) <- c(tmp_names,paste0('c',i))
    
    kappas[i] <- rbinom(1, 80, 0.5)
  }
  
  ## SIMULATE SPATIAL
  dat <- simulatePP(
    agentVarData = dat_use,
    agentKappaData = data.frame(
      "agent" = paste0("c", 1:numCells),
      "clusterAgent" = rep(NA, numCells),
      "kappa" = kappas
    ),
    unitsPerOutcome = 10,
    replicatesPerUnit = 1,
    silent = T
  )
  #dat$replicate <- 1
  
  cells <- paste0("c", 1:numCells)
  cells_interactions <- rbind(
    data.frame(t(combn(cells, 2))),
    data.frame("X1" = cells, "X2" = cells)
  )
  
  pcaData <- getKsPCAData(
    data = dat, replicate = "replicate",
    agents_df = cells_interactions,
    xRange = c(0, 1), yRange = c(0, 1),
    silent = T
  )
  
  pcaData
}
```

The following chunk simulates and plots the results.
```{r fit_plot_alt,eval=FALSE}
totalVars <- c(4, 16, 8, 24)
nTrials <- 100

results_complete <- data.frame()

for(totalVars_idx in 1:length(totalVars)){
  cat(paste0(totalVars[totalVars_idx],': '))
  
  cells <- paste0("c", 1:totalVars[totalVars_idx])
  cells_interactions <- rbind(
    data.frame(t(combn(cells, 2))),
    data.frame("X1" = cells, "X2" = cells)
  )
  
  results <- data.frame('var'=paste0(cells_interactions$X1,'_',cells_interactions$X2),
                        'noise'=0,
                        'int'=0,'both'=0,'total'=0)
  for(i in 1:nTrials){
    cat(paste0(i,', '))
    set.seed(totalVars_idx*1234+i*1234+123456789)
    data <- simulate_Data_numCells_alt(numCells=totalVars[totalVars_idx])
    
    res <- funkyModel(
      data = data,
      outcome = "outcome",
      unit = "unit",
      synthetics = c(100, 100),
      nTrees = 500,
      silent = T,
      K=10
    )
    
    tmp_df <- res$VariableImportance
    tmp_df <- tmp_df[order(-tmp_df$est),]
    results[results$var%in%tmp_df[tmp_df$est >= res$NoiseCutoff,'var'],"noise"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$NoiseCutoff,'var'],"noise"] + 1
    results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff,'var'],"int"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff,'var'],"int"] + 1
    results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                    tmp_df$est >= res$NoiseCutoff ,'var'],"both"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                      tmp_df$est >= res$NoiseCutoff ,'var'],"both"] + 1
    results$total <- results$total + 1
    
  }
  cat(paste0('\n'))
  
  results_complete <- 
    rbind(results_complete,
          cbind(results[,-ncol(results)],'vars'=totalVars[totalVars_idx])
          )
}

# Organize results
results_plot$notImp <- results_plot$var=='c1_c1'


tmp <- results_plot %>%
  filter(!notImp) %>%
  aggregate(both ~ vars,FUN=mean) %>%
  mutate(var='MeanNI')

results_plot1 <-rbind(
  results_plot[results_plot$var=='c1_c1',
               c('var',"both","vars")],
  tmp
)

# Plot 
ggplot(results_plot1) +
  geom_line(aes(x = vars,y=both/100,color=var),
            linewidth=1) +
  geom_point(aes(x = vars,y=both/100,color=var), 
             size=3) +
  theme_bw() +
  theme(legend.text = element_text(size=20),
        legend.title = element_text(size=24),
        axis.text = element_text(size=20),
        axis.title = element_text(size=24)) +
  xlab('Number of Cell Types') +
  ylab('Percent of Detection') +
  labs(color='Var') +
  guides(col='none') +
  ylim(c(0,1)) +
  scale_x_continuous(breaks=c(0,4,8,12,16,20,24))
```


The following code simulates data under the null to specifically examine the false discovery rate.
```{r dev_null}
simulate_Data_numCells_null <- function(seed=NA, numCells=1){
  ## SET SEED
  if(!is.na(seed)){
    set.seed(seed)
  }
  
  dat_use <- data.frame("outcome" = c(0, 1),
                        "c1" = c(1 / 40, 1 / 40))
  kappas <- rep(NA,numCells)
  kappas[1] <- rbinom(1, 80, 0.5)
  for(i in 2:numCells){
    tmp_names <- colnames(dat_use)
    dat_use <- cbind(dat_use,c(1/40, 1/40))
    colnames(dat_use) <- c(tmp_names,paste0('c',i))
    
    kappas[i] <- rbinom(1, 80, 0.5)
  }
  
  ## SIMULATE SPATIAL
  dat <- simulatePP(
    agentVarData = dat_use,
    agentKappaData = data.frame(
      "agent" = paste0("c", 1:numCells),
      "clusterAgent" = rep(NA, numCells),
      "kappa" = kappas
    ),
    unitsPerOutcome = 17,
    replicatesPerUnit = 1,
    silent = T
  )
  #dat$replicate <- 1
  
  cells <- paste0("c", 1:numCells)
  cells_interactions <- rbind(
    data.frame(t(combn(cells, 2))),
    data.frame("X1" = cells, "X2" = cells)
  )
  
  pcaData <- getKsPCAData(
    data = dat, replicate = "replicate",
    agents_df = cells_interactions,
    xRange = c(0, 1), yRange = c(0, 1),
    silent = T
  )
  
  pcaData
}

```

Below runs to code to see false discovery when $$H=100$$.
```{r fit_table100, eval=FALSE}
totalVars <- c(4, 16)
nTrials <- 100

results_complete <- data.frame()
results_list <- results1_list <- list()

for(totalVars_idx in 1:length(totalVars)){
  cat(paste0(totalVars[totalVars_idx],': '))
  
  cells <- paste0("c", 1:totalVars[totalVars_idx])
  cells_interactions <- rbind(
    data.frame(t(combn(cells, 2))),
    data.frame("X1" = cells, "X2" = cells)
  )
  
  results <- data.frame('var'=paste0(cells_interactions$X1,'_',cells_interactions$X2),
                        'noise'=0, 'int'=0,'both'=0,
                        'total'=0,
                        'noiseSD'=0,'intSD'=0,'bothSD'=0)
  results1 <- data.frame()
  for(i in 1:nTrials){
    cat(paste0(i,', '))
    set.seed(totalVars_idx*1234+i*1234+123459)
    data <- simulate_Data_numCells_null(numCells=totalVars[totalVars_idx])
    
    res <- funkyModel(
      data = data,
      outcome = "outcome",
      unit = "unit",
      synthetics = c(100, 100),
      nTrees = 500,
      silent = TRUE,
      K=10
    )
    
    tmp_df <- res$VariableImportance
    tmp_df <- tmp_df[order(-tmp_df$est),]
    results[results$var%in%tmp_df[tmp_df$est >= res$NoiseCutoff,'var'],"noise"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$NoiseCutoff,'var'],"noise"] + 1
    results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff,'var'],"int"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff,'var'],"int"] + 1
    results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                    tmp_df$est >= res$NoiseCutoff ,'var'],"both"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                      tmp_df$est >= res$NoiseCutoff ,'var'],"both"] + 1
    
    results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$NoiseCutoff,'var'],"noiseSD"] <-
      results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$NoiseCutoff,'var'],"noiseSD"] + 1
    results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff,'var'],"intSD"] <-
      results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff,'var'],"intSD"] + 1
    results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff &
                                    tmp_df$est-tmp_df$sd >= res$NoiseCutoff ,'var'],"bothSD"] <-
      results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff &
                                      tmp_df$est-tmp_df$sd >= res$NoiseCutoff ,'var'],"bothSD"] + 1
    results$total <- results$total + 1
    
    results1 <- 
      rbind(results1, 
            data.frame('iter'=i,
                       'numVars'=totalVars[totalVars_idx],
                       'OverNoi'=sum(results$var %in% 
                                       tmp_df[tmp_df$est >= res$NoiseCutoff,'var']),
                       'OverInt'=sum(results$var %in% 
                                       tmp_df[tmp_df$est >= res$InterpolationCutoff,'var']),
                       'OverBot'=sum(results$var %in% 
                                       tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                                tmp_df$est >= res$NoiseCutoff ,'var']),
                       'maxNoi'= as.numeric(tmp_df$est[1] >= res$NoiseCutoff),
                       'maxInt'= as.numeric(tmp_df$est[1] >= res$InterpolationCutoff[1]),
                       'maxBot'= as.numeric(tmp_df$est[1] >= 
                                              max(res$NoiseCutoff,res$InterpolationCutoff[1])),
                       'sdNoi'= sum(results$var %in% 
                                      tmp_df[tmp_df$est-tmp_df$sd >= res$NoiseCutoff,'var']),
                       'sdInt'= sum(results$var %in% 
                                      tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff,'var']),
                       'sdBot'= sum(results$var %in% 
                                      tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff &
                                               tmp_df$est-tmp_df$sd >= res$NoiseCutoff ,'var'])
                       
            ))
  }
  cat(paste0('\n'))

  results_list[[totalVars_idx]] <- results
  results1_list[[totalVars_idx]] <- results1
}

display_res <- data.frame()
for(i in 1:length(totalVars)){
  display_res <- 
    rbind(display_res,
          results1_list[[i]] %>%
            mutate(Noise = OverNoi>0,
                   Interp= OverInt>0,
                   Both = OverBot>0,
                   maxNoise = maxNoi>0,
                   maxInterp= maxInt>0,
                   maxBoth = maxBot>0,
                   sdNoise = sdNoi>0,
                   sdInterp= sdInt>0,
                   sdBoth = sdBot>0) %>%
            group_by(numVars) %>%
            summarise(across(Noise:sdBoth, ~ 
                               mean(., na.rm = TRUE))) %>%
            as.data.frame()
    )
}

display_res100 <- display_res
display_res100
```

Below runs to code to see false discovery when $$H=200$$.
```{r fit_table200, eval=FALSE}
totalVars <- c(4, 16)
nTrials <- 100

results_complete <- data.frame()
results_list <- results1_list <- list()

for(totalVars_idx in 1:length(totalVars)){
  cat(paste0(totalVars[totalVars_idx],': '))
  
  cells <- paste0("c", 1:totalVars[totalVars_idx])
  cells_interactions <- rbind(
    data.frame(t(combn(cells, 2))),
    data.frame("X1" = cells, "X2" = cells)
  )
  
  results <- data.frame('var'=paste0(cells_interactions$X1,'_',cells_interactions$X2),
                        'noise'=0, 'int'=0,'both'=0,
                        'total'=0,
                        'noiseSD'=0,'intSD'=0,'bothSD'=0)
  results1 <- data.frame()
  for(i in 1:nTrials){
    cat(paste0(i,', '))
    set.seed(totalVars_idx*1234+i*1234+123459)
    data <- simulate_Data_numCells_null(numCells=totalVars[totalVars_idx])
    
    res <- funkyModel(
      data = data,
      outcome = "outcome",
      unit = "unit",
      synthetics = c(100, 200),
      nTrees = 500,
      silent = TRUE,
      K=10
    )
    
    tmp_df <- res$VariableImportance
    tmp_df <- tmp_df[order(-tmp_df$est),]
    results[results$var%in%tmp_df[tmp_df$est >= res$NoiseCutoff,'var'],"noise"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$NoiseCutoff,'var'],"noise"] + 1
    results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff,'var'],"int"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff,'var'],"int"] + 1
    results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                    tmp_df$est >= res$NoiseCutoff ,'var'],"both"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                      tmp_df$est >= res$NoiseCutoff ,'var'],"both"] + 1
    
    results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$NoiseCutoff,'var'],"noiseSD"] <-
      results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$NoiseCutoff,'var'],"noiseSD"] + 1
    results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff,'var'],"intSD"] <-
      results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff,'var'],"intSD"] + 1
    results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff &
                                    tmp_df$est-tmp_df$sd >= res$NoiseCutoff ,'var'],"bothSD"] <-
      results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff &
                                      tmp_df$est-tmp_df$sd >= res$NoiseCutoff ,'var'],"bothSD"] + 1
    results$total <- results$total + 1
    
    results1 <- 
      rbind(results1, 
            data.frame('iter'=i,
                       'numVars'=totalVars[totalVars_idx],
                       'OverNoi'=sum(results$var %in% 
                                       tmp_df[tmp_df$est >= res$NoiseCutoff,'var']),
                       'OverInt'=sum(results$var %in% 
                                       tmp_df[tmp_df$est >= res$InterpolationCutoff,'var']),
                       'OverBot'=sum(results$var %in% 
                                       tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                                tmp_df$est >= res$NoiseCutoff ,'var']),
                       'maxNoi'= as.numeric(tmp_df$est[1] >= res$NoiseCutoff),
                       'maxInt'= as.numeric(tmp_df$est[1] >= res$InterpolationCutoff[1]),
                       'maxBot'= as.numeric(tmp_df$est[1] >= 
                                              max(res$NoiseCutoff,res$InterpolationCutoff[1])),
                       'sdNoi'= sum(results$var %in% 
                                      tmp_df[tmp_df$est-tmp_df$sd >= res$NoiseCutoff,'var']),
                       'sdInt'= sum(results$var %in% 
                                      tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff,'var']),
                       'sdBot'= sum(results$var %in% 
                                      tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff &
                                               tmp_df$est-tmp_df$sd >= res$NoiseCutoff ,'var'])
                       
            ))
  }
  cat(paste0('\n'))

  results_list[[totalVars_idx]] <- results
  results1_list[[totalVars_idx]] <- results1
}

display_res <- data.frame()
for(i in 1:length(totalVars)){
  display_res <- 
    rbind(display_res,
          results1_list[[i]] %>%
            mutate(Noise = OverNoi>0,
                   Interp= OverInt>0,
                   Both = OverBot>0,
                   maxNoise = maxNoi>0,
                   maxInterp= maxInt>0,
                   maxBoth = maxBot>0,
                   sdNoise = sdNoi>0,
                   sdInterp= sdInt>0,
                   sdBoth = sdBot>0) %>%
            group_by(numVars) %>%
            summarise(across(Noise:sdBoth, ~ 
                               mean(., na.rm = TRUE))) %>%
            as.data.frame()
    )
}

display_res200 <- display_res
display_res200
```

Below runs to code to see false discovery when $$H=500$$.
```{r fit_table500, eval=FALSE}
totalVars <- c(4, 16)
nTrials <- 100

results_complete <- data.frame()
results_list <- results1_list <- list()

for(totalVars_idx in 1:length(totalVars)){
  cat(paste0(totalVars[totalVars_idx],': '))
  
  cells <- paste0("c", 1:totalVars[totalVars_idx])
  cells_interactions <- rbind(
    data.frame(t(combn(cells, 2))),
    data.frame("X1" = cells, "X2" = cells)
  )
  
  results <- data.frame('var'=paste0(cells_interactions$X1,'_',cells_interactions$X2),
                        'noise'=0, 'int'=0,'both'=0,
                        'total'=0,
                        'noiseSD'=0,'intSD'=0,'bothSD'=0)
  results1 <- data.frame()
  for(i in 1:nTrials){
    cat(paste0(i,', '))
    set.seed(totalVars_idx*1234+i*1234+123459)
    data <- simulate_Data_numCells_null(numCells=totalVars[totalVars_idx])
    
    res <- funkyModel(
      data = data,
      outcome = "outcome",
      unit = "unit",
      synthetics = c(100, 500),
      nTrees = 500,
      silent = TRUE,
      K=10
    )
    
    tmp_df <- res$VariableImportance
    tmp_df <- tmp_df[order(-tmp_df$est),]
    results[results$var%in%tmp_df[tmp_df$est >= res$NoiseCutoff,'var'],"noise"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$NoiseCutoff,'var'],"noise"] + 1
    results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff,'var'],"int"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff,'var'],"int"] + 1
    results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                    tmp_df$est >= res$NoiseCutoff ,'var'],"both"] <-
      results[results$var%in%tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                      tmp_df$est >= res$NoiseCutoff ,'var'],"both"] + 1
    
    results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$NoiseCutoff,'var'],"noiseSD"] <-
      results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$NoiseCutoff,'var'],"noiseSD"] + 1
    results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff,'var'],"intSD"] <-
      results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff,'var'],"intSD"] + 1
    results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff &
                                    tmp_df$est-tmp_df$sd >= res$NoiseCutoff ,'var'],"bothSD"] <-
      results[results$var%in%tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff &
                                      tmp_df$est-tmp_df$sd >= res$NoiseCutoff ,'var'],"bothSD"] + 1
    results$total <- results$total + 1
    
    results1 <- 
      rbind(results1, 
            data.frame('iter'=i,
                       'numVars'=totalVars[totalVars_idx],
                       'OverNoi'=sum(results$var %in% 
                                       tmp_df[tmp_df$est >= res$NoiseCutoff,'var']),
                       'OverInt'=sum(results$var %in% 
                                       tmp_df[tmp_df$est >= res$InterpolationCutoff,'var']),
                       'OverBot'=sum(results$var %in% 
                                       tmp_df[tmp_df$est >= res$InterpolationCutoff &
                                                tmp_df$est >= res$NoiseCutoff ,'var']),
                       'maxNoi'= as.numeric(tmp_df$est[1] >= res$NoiseCutoff),
                       'maxInt'= as.numeric(tmp_df$est[1] >= res$InterpolationCutoff[1]),
                       'maxBot'= as.numeric(tmp_df$est[1] >= 
                                              max(res$NoiseCutoff,res$InterpolationCutoff[1])),
                       'sdNoi'= sum(results$var %in% 
                                      tmp_df[tmp_df$est-tmp_df$sd >= res$NoiseCutoff,'var']),
                       'sdInt'= sum(results$var %in% 
                                      tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff,'var']),
                       'sdBot'= sum(results$var %in% 
                                      tmp_df[tmp_df$est-tmp_df$sd >= res$InterpolationCutoff &
                                               tmp_df$est-tmp_df$sd >= res$NoiseCutoff ,'var'])
                       
            ))
  }
  cat(paste0('\n'))

  results_list[[totalVars_idx]] <- results
  results1_list[[totalVars_idx]] <- results1
}

display_res <- data.frame()
for(i in 1:length(totalVars)){
  display_res <- 
    rbind(display_res,
          results1_list[[i]] %>%
            mutate(Noise = OverNoi>0,
                   Interp= OverInt>0,
                   Both = OverBot>0,
                   maxNoise = maxNoi>0,
                   maxInterp= maxInt>0,
                   maxBoth = maxBot>0,
                   sdNoise = sdNoi>0,
                   sdInterp= sdInt>0,
                   sdBoth = sdBot>0) %>%
            group_by(numVars) %>%
            summarise(across(Noise:sdBoth, ~ 
                               mean(., na.rm = TRUE))) %>%
            as.data.frame()
    )
}

display_res500 <- display_res
display_res500
```
