---
title: "TNBC"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TNBC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

```{r setup}
  library(funkycells)
```

This vignette documents a sample analysis of Triple Negative Breast Cancer (TNBC) data, retrieved from \url{https://www.angelolab.com/mibi-data}. The data has been preloaded into this package. The following two data sets are retrieved.
```{r getData}
  TNBC <- TNBC
  TNBC_Meta <- TNBC_Meta
```

We recommend exploring this data, and additional information is available in the data documentation. Such analysis reveals TNBC contains the cell information while TNBC_Meta contains the metadata. 

Diagram Info
```{r diagram}
## Data Gen
set.seed(12345)
dat0 <- simulatePP(cellVarData=
                       data.frame('stage'=c(0,1),
                                  'A'=c(0,0),
                                  'B'=c(1/50,1/1000)),
                   cellKappaData=data.frame(
                                  'cell'=c('A','B'),
                                  'clusterCell'=c(NA,'A'),
                                  'kappa'=c(20,5)),
                   peoplePerStage=50,
                   imagesPerPerson=1,
                   silent=F )
dat1 <- simulatePP(cellVarData=
                     data.frame('stage'=c(0,1),
                                'A'=c(0,0),
                                'B'=c(1/50,1/50)),
                   cellKappaData=data.frame(
                                 'cell'=c('A','B'),
                                 'clusterCell'=c(NA,'A'),
                                 'kappa'=c(20,5)),
                   peoplePerStage=1,
                   imagesPerPerson=1,
                   silent=F)
dat1$Person <- ifelse(dat1$Person=='p1','p101',
                      ifelse(dat1$Person=='p2','p102', NA))
dat1$Image <- ifelse(dat1$Image=='1','101',
                     ifelse(dat1$Image=='2','102',NA))
dat <- rbind(dat0,dat1)

set.seed(12345)
Kvals <- getKFunction(data = dat[,-1], agents = c('A','B'),
             unit = 'Person', repeatedUniqueId = 'Image',
             xRange = c(0,1), yRange = c(0,1),
             rCheckVals = seq(0,0.25,0.01))
pcaData <- getPCAData(dat,repeatedUniqueId='Image',
                      xRange = c(0,1),  yRange = c(0,1),
                      silent=F)

set.seed(12345)
pcaMeta <- simulateMeta(pcaData,
                        metaInfo = data.frame(
                          'var'=c('randUnif','randBin','corrNorm'),
                          'rdist'=c('runif','rbinom','rnorm'),
                          'Stage_0'=c('0.5','0.5','1'),
                          'Stage_1'=c('0.5','0.5','2')))

set.seed(12345)
rfcv <- computeRandomForest_CVPC(data=pcaMeta,repeatedId='Image',
                                 metaNames=c('randUnif','randBin','corrNorm'),
                                 cellData=dat)

## K FUNCTIONS
ggplot() +
  geom_line(aes(x=r,y=K1),data=Kvals, size=2) +
  theme_bw() +
  theme(axis.title = element_blank(),
        axis.text = element_blank())
ggplot() +
  geom_line(aes(x=r,y=K52),data=Kvals, size=2) +
  theme_bw() +
  theme(axis.title = element_blank(),
        axis.text = element_blank())

## Point Processes
plotPP(dat[dat$Image==1,c('x','y','cellType')],
       ptSize = 5, dropAxes = T, colorGuide = 'none')
plotPP(dat[dat$Image==51,c('x','y','cellType')],
       ptSize = 5, dropAxes = T, colorGuide = 'none')
plotPP(dat[dat$Image==60,c('x','y','cellType')],
       ptSize = 5, dropAxes = T, colorGuide = 'none')

## RF
giniData=rfcv$Gini 
viData=rfcv$VI
accData=rfcv$Accuracy
noiseMap=rfcv$AddDataToCVVarImpPlot$noiseMap 
KFunctions=rfcv$AddDataToCVVarImpPlot$KFunctions
metaNames=rfcv$AddDataToCVVarImpPlot$metaNames
alpha=rfcv$AddDataToCVVarImpPlot$alpha 
alignmentMethod = 'Mult'
curveData=rfcv$AddDataToCVVarImpPlot$curveData
subsetPlotSize=rfcv$AddDataToCVVarImpPlot$subsetPlotSize

## .generateCVVariableImportancePlot
set.seed(12345)
cutoffs <- .getIndividualCutoffs(noiseMap,giniData,viData,alignmentMethod,
                                 alpha)

standardizedData <- .standardizeVarImpData(giniData, viData,
                                           KFunctions, metaNames,
                                           cutoffs$giniCutoff_df,
                                           cutoffs$viCutoff_df,
                                           alignmentMethod)

## Full
underlyingData = standardizedData$stdVI
ylabel = 'Variable Importance'
cutoff = max(cutoffs$viCutoff_df$cutoff)
curveDat = curveData[,2]

## .plotCVVariableImportance
maxVal <- max(underlyingData$avgVal,curveDat)
ggplot2::ggplot(data=underlyingData,
                mapping=ggplot2::aes(x=factor(reorder(var,avgVal)),
                                     y=ifelse(avgVal/maxVal>1,1,
                                              ifelse(avgVal/maxVal<0,0,
                                                     avgVal/maxVal)),
                                     group=1)) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin=ifelse((avgVal-sd)/maxVal<0,0,(avgVal-sd)/maxVal),
                                      ymax = ifelse((avgVal+sd)/maxVal>1,1,(avgVal+sd)/maxVal)),
                         color='darkgray', width=0.2,size=1.5) +
  ggplot2::geom_point(color='black',size=3) +
  ggplot2::geom_hline(ggplot2::aes(yintercept=max(0,min(1,cutoff/maxVal))),
                      color='red', linetype='dotted',linewidth=2) +
  ggplot2::coord_flip(ylim = c(0,1)) +
  ggplot2::xlab(NULL) + #'Variables') +
  ggplot2::ylim(c(0,1)) +
  ggplot2::ylab(NULL) +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text=ggplot2::element_text(size=18),
                 axis.ticks.y=ggplot2::element_blank(),
                 panel.grid.major.y = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(size=22)) +
  ggplot2::geom_line(ggplot2::aes(
    x=ordered(underlyingData[order(-avgVal),'var']),
    y=curveDat/maxVal),color='orange', linetype='dashed',size=2) +
  ggplot2::ylab(paste0('OOB (',
                       .specify_decimal(accData$OOB,2),
                       '), Guess (',
                       .specify_decimal(accData$guess,2),
                       '), Bias (',
                       .specify_decimal(accData$bias,2),')'))

######## Fake Synthetic 
data=pcaMeta
outcome='Stage'
unit='Person'
repeatedId='Image'
metaNames=c('randUnif','randBin','corrNorm')
cellData=dat
syntheticKs = 100

set.seed(12345)
NamesPCs <- .getUnderlyingNamesAndPCsCount(
  colnames(data)[!(colnames(data)%in%
                     c(outcome, unit, repeatedId, metaNames))])

noiseMap <- NULL

if(!is.null(cellData[['cellType']])){
  kappa <- round(mean(table(cellData[,'cellType'])) /
                   nrow(unique(cellData[,c(outcome, unit, repeatedId)])))
} else{
  kappa <- (sum(cellData[
    unique(stringr::str_remove_all(NamesPCs$Vars,'_.*$'))]) /
      length(NamesPCs$Vars) ) /
    nrow(unique(cellData[,c(outcome, unit, repeatedId)]))
}

noiseData <- .generateKNoiseGroup(
  syntheticKs = syntheticKs, cellData = cellData,
  agentName='syntheticCell',
  kappaL = kappa, kappaR=kappa,
  outcome = outcome, unit = unit,
  repeatedId = repeatedId)


Kvals_n <- getKFunction(data = noiseData[,-4], agents = c('syntheticCell1L','syntheticCell1R'),
                        unit = 'Person', repeatedUniqueId = 'Image',
                        xRange = c(0,1), yRange = c(0,1),
                        rCheckVals = seq(0,0.25,0.01))

## K FUNCTIONS
ggplot() +
  geom_line(aes(x=r,y=K1),data=Kvals_n, size=2) +
  theme_bw() +
  theme(axis.title = element_blank(),
        axis.text = element_blank())
ggplot() +
  geom_line(aes(x=r,y=K52),data=Kvals_n, size=2) +
  theme_bw() +
  theme(axis.title = element_blank(),
        axis.text = element_blank())

## Point Processes
plotPP(noiseData[noiseData$Image==1 & 
                   noiseData$cellType %in% c('syntheticCell1L','syntheticCell1R'),
                 c('x','y','cellType')],
       ptSize = 5, dropAxes = T, colorGuide = 'none')
plotPP(noiseData[noiseData$Image==52 & 
                   noiseData$cellType %in% c('syntheticCell1L','syntheticCell1R'),
                 c('x','y','cellType')],
       ptSize = 5, dropAxes = T, colorGuide = 'none')


```


Exploring the data, we can build simulations with similar behaviors.
```{r simNoEffect}

set.seed(12345)
dat0 <- simulatePP(cellVarData=
                     data.frame('stage'=c(0,1),
                                'c1'=c(0,0),
                                'c2'=c(1/25,1/25), 'c3'=c(1/50,1/50),
                                'c4'=c(0,0),
                                'c5'=c(0,0),'c6'=c(0,0),
                                'c7'=c(0,0),'c8'=c(1/100,1/100),
                                'c9'=c(1/20,1/20), 'c10'=c(1/250,1/250),
                                'c11'=c(1/100,1/100),'c12'=c(1/80,1/80),
                                'c13'=c(0,0),'c14'=c(0,0),
                                'c15'=c(0,0),'c16'=c(0,0),
                                'c17'=c(0,0),'c18'=c(0,0)),
                   cellKappaData=data.frame(
                     'cell'=paste0('c',1:18),
                     'clusterCell'=c(NA,'c1','c1', rep(NA,15)),
                     'kappa'=c(rbinom(1,100,0.5),
                               rbinom(2,70,0.5),
                               rbinom(1,60,0.5),
                               rbinom(2,300,0.5),
                               rbinom(2,120,0.5),
                               rbinom(4,600,0.5),
                               rbinom(2,120,0.5),
                               rbinom(2,50,0.5),
                               rbinom(2,20,0.5))),
                   peoplePerStage=17,
                   imagesPerPerson=1,
                   silent=F)
dat1 <- simulatePP(cellVarData=
                     data.frame('stage'=c(0,1),
                                'c1'=c(0,0),
                                'c2'=c(1/25,1/25), 'c3'=c(1/50,1/50),
                                'c4'=c(0,0),
                                'c5'=c(0,0),'c6'=c(0,0),
                                'c7'=c(0,0),'c8'=c(1/100,1/100),
                                'c9'=c(1/20,1/20), 'c10'=c(1/250,1/250),
                                'c11'=c(1/100,1/100),'c12'=c(1/80,1/80),
                                'c13'=c(0,0),'c14'=c(0,0),
                                'c15'=c(0,0),'c16'=c(0,0),
                                'c17'=c(0,0),'c18'=c(0,0)),
                   cellKappaData=data.frame(
                     'cell'=paste0('c',1:18),
                     'clusterCell'=c(NA,'c1','c1', rep(NA,15)),
                     'kappa'=c(rbinom(1,100,0.5),
                               rbinom(2,70,0.5),
                               rbinom(1,60,0.5),
                               rbinom(2,300,0.5),
                               rbinom(2,120,0.5),
                               rbinom(4,600,0.5),
                               rbinom(2,120,0.5),
                               rbinom(2,50,0.5),
                               rbinom(2,20,0.5))),
                   peoplePerStage=1,
                   imagesPerPerson=1,
                   silent=F)
dat1$Person <- ifelse(dat1$Person=='p1','p35',
                      ifelse(dat1$Person=='p2','p36', NA))
dat1$Image <- ifelse(dat1$Image=='1','35',
                     ifelse(dat1$Image=='2','36',NA))
dat <- rbind(dat0,dat1)
set.seed(12345)
pcaData <- getPCAData(data = dat,repeatedUniqueId='Image',
                      xRange = c(0,1),  yRange = c(0,1),
                      silent=F)
set.seed(12345)
pcaMeta <- simulateMeta(pcaData,
                        metaInfo = data.frame(
                          'var'=c('gender','age'),
                          'rdist'=c('rbinom','rnorm'),
                          'Stage_0'=c('0.5','25'),
                          'Stage_1'=c('0.5','25')))
set.seed(12345)
rfcv <- computeRandomForest_CVPC(data=pcaMeta,#pcaMetaCt$data,
                                 outcome = 'Stage',
                                 unit = 'Person',repeatedId='Image',
                                 metaNames=c('gender','age'),
                                 cellData=dat)
rfcv$multIntVI$subset_viPlot
rfcv$multIntVI$viPlot

```

```{r simEffect}

set.seed(12345)
dat0 <- simulatePP(cellVarData=
                     data.frame('stage'=c(0,1),
                                'c1'=c(0,0),
                                'c2'=c(1/25,1/60), 'c3'=c(1/50,1/10),
                                'c4'=c(0,0),
                                'c5'=c(0,0),'c6'=c(0,0),
                                'c7'=c(0,0),'c8'=c(1/100,1/100),
                                'c9'=c(1/20,1/20), 'c10'=c(1/250,1/250),
                                'c11'=c(1/100,1/100),'c12'=c(1/80,1/80),
                                'c13'=c(0,0),'c14'=c(0,0),
                                'c15'=c(0,0),'c16'=c(0,0),
                                'c17'=c(0,0),'c18'=c(0,0)),
                   cellKappaData=data.frame(
                     'cell'=paste0('c',1:18),
                     'clusterCell'=c(NA,'c1','c1', rep(NA,15)),
                     'kappa'=c(rbinom(1,100,0.5),
                               rbinom(2,70,0.5),
                               rbinom(1,60,0.5),
                               rbinom(2,300,0.5),
                               rbinom(2,120,0.5),
                               rbinom(4,600,0.5),
                               rbinom(2,120,0.5),
                               rbinom(2,50,0.5),
                               rbinom(2,20,0.5))),
                   peoplePerStage=17,
                   imagesPerPerson=1,
                   silent=F)
dat1 <- simulatePP(cellVarData=
                     data.frame('stage'=c(0,1),
                                'c1'=c(0,0),
                                'c2'=c(1/25,1/25), 'c3'=c(1/50,1/50),
                                'c4'=c(0,0),
                                'c5'=c(0,0),'c6'=c(0,0),
                                'c7'=c(0,0),'c8'=c(1/100,1/100),
                                'c9'=c(1/20,1/20), 'c10'=c(1/250,1/250),
                                'c11'=c(1/100,1/100),'c12'=c(1/80,1/80),
                                'c13'=c(0,0),'c14'=c(0,0),
                                'c15'=c(0,0),'c16'=c(0,0),
                                'c17'=c(0,0),'c18'=c(0,0)),
                   cellKappaData=data.frame(
                     'cell'=paste0('c',1:18),
                     'clusterCell'=c(NA,'c1','c1', rep(NA,15)),
                     'kappa'=c(rbinom(1,100,0.5),
                               rbinom(2,70,0.5),
                               rbinom(1,60,0.5),
                               rbinom(2,300,0.5),
                               rbinom(2,120,0.5),
                               rbinom(4,600,0.5),
                               rbinom(2,120,0.5),
                               rbinom(2,50,0.5),
                               rbinom(2,20,0.5))),
                   peoplePerStage=2,
                   imagesPerPerson=1,
                   silent=F)
dat1$Person <- ifelse(dat1$Person=='p1','p35',
                      ifelse(dat1$Person=='p2','p36',
                             ifelse(dat1$Person=='p3','p37',
                                    ifelse(dat1$Person=='p4','p38',NA))))
dat1$Image <- ifelse(dat1$Image=='1','35',
                     ifelse(dat1$Image=='2','36',
                            ifelse(dat1$Image=='3','37',
                                   ifelse(dat1$Image=='4','38',NA))))
dat <- rbind(dat0,dat1)
set.seed(12345)
pcaData <- getPCAData(data = dat,repeatedUniqueId='Image',
                      xRange = c(0,1),  yRange = c(0,1),
                      silent=F)
set.seed(12345)
pcaMeta <- simulateMeta(pcaData,
                        metaInfo = data.frame(
                          'var'=c('gender','age'),
                          'rdist'=c('rbinom','rnorm'),
                          'Stage_0'=c('0.5','25'),
                          'Stage_1'=c('0.5','27.5')))
set.seed(12345)
rfcv <- computeRandomForest_CVPC(data=pcaMeta,#pcaMetaCt$data,
                                 outcome = 'Stage',
                                 unit = 'Person',repeatedId='Image',
                                 metaNames=c('gender','age'),
                                 cellData=dat)
rfcv$multIntVI$subset_viPlot
rfcv$multIntVI$viPlot

```

```{r plotSimEffect}
# saveRDS(rfcv,'C:/Users/jerem/Downloads/Paper/SeeMe/rfcv_Effect.rds')

giniData=rfcv$Gini 
viData=rfcv$VI
accData=rfcv$Accuracy
noiseMap=rfcv$AddDataToCVVarImpPlot$noiseMap 
KFunctions=rfcv$AddDataToCVVarImpPlot$KFunctions
metaNames=rfcv$AddDataToCVVarImpPlot$metaNames
alpha=rfcv$AddDataToCVVarImpPlot$alpha 
alignmentMethod = 'Mult'
curveData=rfcv$AddDataToCVVarImpPlot$curveData
subsetPlotSize=rfcv$AddDataToCVVarImpPlot$subsetPlotSize

## .generateCVVariableImportancePlot

cutoffs <- .getIndividualCutoffs(noiseMap,giniData,viData,alignmentMethod,
                                 alpha)

standardizedData <- .standardizeVarImpData(giniData, viData,
                                           KFunctions, metaNames,
                                           cutoffs$giniCutoff_df,
                                           cutoffs$viCutoff_df,
                                           alignmentMethod)

## Full
underlyingData = standardizedData$stdVI
ylabel = 'Variable Importance'
cutoff = max(cutoffs$viCutoff_df$cutoff)
curveDat = curveData[,2]

## .plotCVVariableImportance
maxVal <- max(underlyingData$avgVal,curveDat)
ggplot2::ggplot(data=underlyingData,
                mapping=ggplot2::aes(x=factor(reorder(var,avgVal)),
                                     y=ifelse(avgVal/maxVal>1,1,
                                              ifelse(avgVal/maxVal<0,0,
                                                     avgVal/maxVal)),
                                     group=1)) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin=ifelse((avgVal-sd)/maxVal<0,0,(avgVal-sd)/maxVal),
                                      ymax = ifelse((avgVal+sd)/maxVal>1,1,(avgVal+sd)/maxVal)),
                         color='darkgray', width=0.2) +
  ggplot2::geom_point(color='black') +
  ggplot2::geom_hline(ggplot2::aes(yintercept=max(0,min(1,cutoff/maxVal))),
                      color='red', linetype='dotted',linewidth=2) +
  ggplot2::coord_flip(ylim = c(0,1)) +
  ggplot2::xlab(NULL) +#'Variables') +
  ggplot2::ylim(c(0,1)) +
  ggplot2::ylab(NULL) +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text.y=ggplot2::element_blank(),
                 axis.ticks.y=ggplot2::element_blank(),
                 panel.grid.major.y = ggplot2::element_blank(),
                 axis.text.x = ggplot2::element_text(size=18),
                 axis.title = ggplot2::element_text(size=22)) +
  ggplot2::geom_line(ggplot2::aes(
    x=ordered(underlyingData[order(-avgVal),'var']),
    y=curveDat/maxVal),color='orange', linetype='dashed',size=2)


## Subset

tmpStdGini <- standardizedData$stdGini[order(-standardizedData$stdGini$avg),]
tmpStdVI <- standardizedData$stdVI[order(-standardizedData$stdVI$avg),]

underlyingData = tmpStdVI[1:subsetPlotSize,]
ylabel = 'Variable Importance'
cutoff = max(cutoffs$viCutoff_df$cutoff)
curveDat =curveData[1:subsetPlotSize,2]


## .plotCVVariableImportance
maxVal <- max(underlyingData$avgVal,curveDat)
ggplot2::ggplot(data=underlyingData,
                mapping=ggplot2::aes(x=factor(reorder(var,avgVal)),
                                     y=ifelse(avgVal/maxVal>1,1,
                                              ifelse(avgVal/maxVal<0,0,
                                                     avgVal/maxVal)),
                                     group=1)) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin=ifelse((avgVal-sd)/maxVal<0,0,(avgVal-sd)/maxVal),
                                      ymax = ifelse((avgVal+sd)/maxVal>1,1,(avgVal+sd)/maxVal)),
                         color='darkgray', width=0.4, size=1.5) +
  ggplot2::geom_point(color='black', size=3) +
  ggplot2::geom_hline(ggplot2::aes(yintercept=max(0,min(1,cutoff/maxVal))),
                      color='red', linetype='dotted',linewidth=2) +
  ggplot2::coord_flip(ylim = c(0,1)) +
  ggplot2::xlab(NULL) +
  ggplot2::ylim(c(0,1)) +
  ggplot2::ylab(NULL) +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text=ggplot2::element_text(size=18),
                 axis.ticks.y=ggplot2::element_blank(),
                 panel.grid.major.y = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(size=22)) +
  ggplot2::geom_line(ggplot2::aes(
    x=ordered(underlyingData[order(-avgVal),'var']),
    y=curveDat/maxVal),color='orange', linetype='dashed',size=2) +
  ggplot2::ylab(paste0('OOB (',
                       .specify_decimal(accData$OOB,2),
                       '), Guess (',
                       .specify_decimal(accData$guess,2),
                       '), Bias (',
                       .specify_decimal(accData$bias,2),')'))
```

Also look at similar structure 
```{r structure}
set.seed(12345)
dat0 <- simulatePP(cellVarData=
                     data.frame('stage'=c(0,1),
                                'c1'=c(0,0),
                                'c2'=c(1/25,1/60), 'c3'=c(1/50,1/25),
                                'c4'=c(0,0),
                                'c5'=c(0,0),'c6'=c(0,0),
                                'c7'=c(0,0),'c8'=c(1/100,1/100),
                                'c9'=c(1/20,1/20), 'c10'=c(1/250,1/250),
                                'c11'=c(1/100,1/100),'c12'=c(1/80,1/80),
                                'c13'=c(0,0),'c14'=c(0,0),
                                'c15'=c(0,0),'c16'=c(0,0),
                                'c17'=c(0,0),'c18'=c(0,0)),
                   cellKappaData=data.frame(
                     'cell'=paste0('c',1:18),
                     'clusterCell'=c(NA,'c1','c1', rep(NA,15)),
                     'kappa'=c(rbinom(1,100,0.5),
                               rbinom(2,70,0.5),
                               rbinom(1,60,0.5),
                               rbinom(2,300,0.5),
                               rbinom(2,120,0.5),
                               rbinom(4,600,0.5),
                               rbinom(2,120,0.5),
                               rbinom(2,50,0.5),
                               rbinom(2,20,0.5))),
                   peoplePerStage=17,
                   imagesPerPerson=1,
                   silent=F)
dat1 <- simulatePP(cellVarData=
                     data.frame('stage'=c(0,1),
                                'c1'=c(0,0),
                                'c2'=c(1/25,1/25), 'c3'=c(1/50,1/50),
                                'c4'=c(0,0),
                                'c5'=c(0,0),'c6'=c(0,0),
                                'c7'=c(0,0),'c8'=c(1/100,1/100),
                                'c9'=c(1/20,1/20), 'c10'=c(1/250,1/250),
                                'c11'=c(1/100,1/100),'c12'=c(1/80,1/80),
                                'c13'=c(0,0),'c14'=c(0,0),
                                'c15'=c(0,0),'c16'=c(0,0),
                                'c17'=c(0,0),'c18'=c(0,0)),
                   cellKappaData=data.frame(
                     'cell'=paste0('c',1:18),
                     'clusterCell'=c(NA,'c1','c1', rep(NA,15)),
                     'kappa'=c(rbinom(1,100,0.5),
                               rbinom(2,70,0.5),
                               rbinom(1,60,0.5),
                               rbinom(2,300,0.5),
                               rbinom(2,120,0.5),
                               rbinom(4,600,0.5),
                               rbinom(2,120,0.5),
                               rbinom(2,50,0.5),
                               rbinom(2,20,0.5))),
                   peoplePerStage=1,
                   imagesPerPerson=1,
                   silent=F)
dat1$Person <- ifelse(dat1$Person=='p1','p35',
                      ifelse(dat1$Person=='p2','p36', NA))
#                             ifelse(dat1$Person=='p3','p37',
#                                    ifelse(dat1$Person=='p4','p38',NA))))
dat1$Image <- ifelse(dat1$Image=='1','35',
                     ifelse(dat1$Image=='2','36',NA))
#                             ifelse(dat1$Image=='3','37',
#                                    ifelse(dat1$Image=='4','38',NA))))
dat <- rbind(dat0,dat1)
set.seed(12345)
pcaData <- getPCAData(data = dat,repeatedUniqueId='Image',
                      xRange = c(0,1),  yRange = c(0,1),
                      silent=F)
set.seed(12345)
pcaMeta <- simulateMeta(pcaData,
                        metaInfo = data.frame(
                          'var'=c('gender','age'),
                          'rdist'=c('rbinom','rnorm'),
                          'Stage_0'=c('0.5','25'),
                          'Stage_1'=c('0.5','27.5')))
set.seed(12345)
rfcv <- computeRandomForest_CVPC(data=pcaMeta,#pcaMetaCt$data,
                                 outcome = 'Stage',
                                 unit = 'Person',repeatedId='Image',
                                 #metaNames=c(pcaMetaCt$metaNames,'gender','age'),
                                 metaNames=c('gender','age'),
                                 cellData=dat)
rfcv$multIntVI$subset_viPlot
rfcv$multIntVI$viPlot
```

Now returning to the data, the first step is to convert the cell data into K functions. This data is unique since rather than giving a cell type, a T/F column is given for different columns. Therefore, the K functions, discritized using PCA is computed as follows.
```{r computePCA}
  proteins <- c("FoxP3","Lag3","CD4","CD16","CD56","PD1","PD.L1",
                             "Ki67","CD138","CD68","CD8","CD3","IDO","CD45RO",
                             "CD20","p53","MPO","tumorYN")
  agents_df <- expand.grid(proteins, proteins)
  dataPCA <- getPCAData(data = TNBC[,-3], unit='Person', agents_df=agents_df, rCheckVals = seq(0,50,1))
```

The resulting data is merged with the meta data for use in analysis.
```{r addMeta}
  dataPCAAge  <- merge(dataPCA,TNBC_Meta)
```

We then compute the cross-validated random forest.
```{r computeRFCV}
  rfcv <- computeRandomForest_CVPC(data=dataPCAAge, K=10, outcome='Class',unit='Person',repeatedId=NULL, metaNames=c('Age'),cellData= TNBC[,-3], synthetics=100, generalSyntheticK=T, alpha=0.05,curvedSigSims = 100, silent=F,subsetPlotSize = 25, nTrees=500)
```

And finally the resulting plots-both full and subsetted--can be examined.
```{r viewFullPlot, fig.width=10, fig.height=11, fig.cap="All Variables"}
  rfcv$multIntVI$viPlot
```

```{r viewSubPlot, fig.width=10, fig.height=11, fig.cap="Top 25 Variables"}
  rfcv$multIntVI$subset_viPlot
```

I use the following code to improve plots
```{r, improvedPlots}
# saveRDS(rfcv,'C:/Users/jerem/Downloads/Paper/UpdatedCode/rfcv_Effect.rds')

giniData=rfcv$Gini 
viData=rfcv$VI
accData=rfcv$Accuracy
noiseMap=rfcv$AddDataToCVVarImpPlot$noiseMap 
KFunctions=rfcv$AddDataToCVVarImpPlot$KFunctions
metaNames=rfcv$AddDataToCVVarImpPlot$metaNames
alpha=rfcv$AddDataToCVVarImpPlot$alpha 
alignmentMethod = 'Mult'
curveData=rfcv$AddDataToCVVarImpPlot$curveData
subsetPlotSize=rfcv$AddDataToCVVarImpPlot$subsetPlotSize

## .generateCVVariableImportancePlot

cutoffs <- .getIndividualCutoffs(noiseMap,viData,alignmentMethod,
                                 alpha)

standardizedData <- .standardizeVarImpData(viData,
                                           KFunctions, metaNames,
                                           cutoffs$viCutoff_df,
                                           alignmentMethod)

## Full
underlyingData = standardizedData$stdVI
ylabel = 'Variable Importance'
cutoff = max(cutoffs$viCutoff_df$cutoff)
curveDat = curveData[,2]

## .plotCVVariableImportance
maxVal <- max(underlyingData$avgVal,curveDat)
ggplot2::ggplot(data=underlyingData,
                mapping=ggplot2::aes(x=factor(reorder(var,avgVal)),
                                     y=ifelse(avgVal/maxVal>1,1,
                                              ifelse(avgVal/maxVal<0,0,
                                                     avgVal/maxVal)),
                                     group=1)) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin=ifelse((avgVal-sd)/maxVal<0,0,(avgVal-sd)/maxVal),
                                      ymax = ifelse((avgVal+sd)/maxVal>1,1,(avgVal+sd)/maxVal)),
                         color='darkgray', width=0.2) +
  ggplot2::geom_point(color='black') +
  ggplot2::geom_hline(ggplot2::aes(yintercept=max(0,min(1,cutoff/maxVal))),
                      color='red', linetype='dotted',linewidth=2) +
  ggplot2::coord_flip(ylim = c(0,1)) +
  ggplot2::xlab(NULL) +#'Variables') +
  ggplot2::ylim(c(0,1)) +
  ggplot2::ylab(NULL) +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text.y=ggplot2::element_blank(),
                 axis.ticks.y=ggplot2::element_blank(),
                 panel.grid.major.y = ggplot2::element_blank(),
                 axis.text.x = ggplot2::element_text(size=18),
                 axis.title = ggplot2::element_text(size=22)) +
  ggplot2::geom_line(ggplot2::aes(
    x=ordered(underlyingData[order(-avgVal),'var']),
    y=curveDat/maxVal),color='orange', linetype='dashed',size=2)


## Subset

tmpStdVI <- standardizedData$stdVI[order(-standardizedData$stdVI$avg),]

underlyingData = tmpStdVI[1:subsetPlotSize,]
ylabel = 'Variable Importance'
cutoff = max(cutoffs$viCutoff_df$cutoff)
curveDat =curveData[1:subsetPlotSize,2]


## .plotCVVariableImportance
maxVal <- max(underlyingData$avgVal,curveDat)
ggplot2::ggplot(data=underlyingData,
                mapping=ggplot2::aes(x=factor(reorder(var,avgVal)),
                                     y=ifelse(avgVal/maxVal>1,1,
                                              ifelse(avgVal/maxVal<0,0,
                                                     avgVal/maxVal)),
                                     group=1)) +
  ggplot2::geom_errorbar(ggplot2::aes(ymin=ifelse((avgVal-sd)/maxVal<0,0,(avgVal-sd)/maxVal),
                                      ymax = ifelse((avgVal+sd)/maxVal>1,1,(avgVal+sd)/maxVal)),
                         color='darkgray', width=0.4, size=1.5) +
  ggplot2::geom_point(color='black', size=3) +
  ggplot2::geom_hline(ggplot2::aes(yintercept=max(0,min(1,cutoff/maxVal))),
                      color='red', linetype='dotted',linewidth=2) +
  ggplot2::coord_flip(ylim = c(0,1)) +
  ggplot2::xlab(NULL) +
  ggplot2::ylim(c(0,1)) +
  ggplot2::ylab(NULL) +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text=ggplot2::element_text(size=18),
                 axis.ticks.y=ggplot2::element_blank(),
                 panel.grid.major.y = ggplot2::element_blank(),
                 axis.title = ggplot2::element_text(size=22)) +
  ggplot2::geom_line(ggplot2::aes(
    x=ordered(underlyingData[order(-avgVal),'var']),
    y=curveDat/maxVal),color='orange', linetype='dashed',size=2) +
  ggplot2::ylab(paste0('OOB (',
                       .specify_decimal(accData$OOB,2),
                       '), Guess (',
                       .specify_decimal(accData$guess,2),
                       '), Bias (',
                       .specify_decimal(accData$bias,2),')'))



```
